One Step Closer to Version 1.0

### 2018-03-25 GSoC/GSoC.tex
GSoC: Edited files for GSoC proposal
Signed-off-by: Rohit Das <rohit.das950@gmail.com>
GSoC: Changed timeline a bit
Signed-off-by: Rohit Das <rohit.das950@gmail.com>

% Customizing footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\leftline{GSoC KDE 2018}}%
% \let\@evenfoot\@oddfoot
% }
%\makeatother

@@

					\item {They will use the above sources in a circuit and see how it works. Separate levels shall be dedicated initially to teaching how the sources work and how they differ. The arrows showing direction of current shall be very helpful in this case. In later levels, both sources shall be kept(in separate levels) to teach them how components work with each source.}

@@

					\item {For showing the resistance, current and voltage flowing across circuits, Kirchoff’s law will be used. Each component shall have separate functions to keep track of individual current flowing through it. Using that, the overall resistance, current and voltage in the circuit can be calculated. Details of the calculation will be beyond the comprehension of the children, and hence hidden from users.}

@@

{May 25 - June 10} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Test out codes from external libraries, and start implementing basic components without classes

@@

		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
	\end{itemize}
\end{itemize}
}\\
\hline

%{June 16 - June 25} & \par
%\parbox{12cm}{
%\begin{itemize}[noitemsep, topsep=2pt]
	%\begin{itemize}[noitemsep, topsep=2pt]
		%\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
	%\end{itemize}
%\end{itemize}
%}\\
%\hline

 & \par
 \parbox{12cm}{
	\begin{itemize}[noitemsep, topsep=2pt]
		\item 
		\begin{itemize}[noitemsep, topsep=2pt]
			\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
		\end{itemize}
	\end{itemize}	 
 }\\
 \hline

@@

\end{tabularx}
\end{center}
\bigskip\bigskip

@@

\item {Added option to change case of letter to find in Letter-In-Word activity:\\
\href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
\end{itemize}
\bigskip
\textbf{Website: }\href{mouri11.github.io}{mouri11.github.io}\\
\textbf{Contact Info:}\\
\textbf{Email: }{rohit.das950@gmail.com}\\
\textbf{IRC Nick: } mouri11

>>>>

% Customizing footer
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\leftline{\textit{GSoC KDE 2018 \hspace{115mm}\today}}}
 \let\@evenfoot\@oddfoot
 }
\makeatother

@@

					\item {They will use the above sources in a circuit and see how it works. Separate levels shall be dedicated initially to teaching how the sources work and how they differ (explained in next point). The arrows showing direction of current shall be very helpful in this case. In later levels, both sources shall be kept(in separate levels) to teach them how components work with each source.}

					\item {To teach the differences between the sources, waveforms will be helpful to show the physical difference. The arrows, as mentioned above, shall show how the direction changes with time in AC, but not in DC. The origin of the sources, i.e., dry cells for DC and power plugs for AC will also be helpful for children to distinguish between them.}

@@

					\item {In free mode, for showing the resistance, current and voltage flowing across circuits, Kirchoff’s law(for DC) will be used. All the components will be iterated through before calculating individual voltages and currents. Details of the calculation will be beyond the comprehension of the children, and hence hidden from users.}

					\item {For solving complicated mathematical equations to obtain current and voltages across circuits(complex numbers for AC), QtMath (\href{http://doc.qt.io/qt-5/qtmath.html}{http://doc.qt.io/qt-5/qtmath.html}) header can be used for basic exponential, logarithmic and trigonometric calculations. For more complex calculations (and matrix manipulations if necessary), math.js (\href{http://mathjs.org/}{http://mathjs.org/}) is a good alternative.}

@@

{May 27 - June 10} & \par
\parbox{12cm}{
\begin{itemize}[noitemsep, topsep=2pt]
	\item Test out codes from external libraries, and start implementing basic components without classes

@@

	\end{itemize}
\end{itemize}
}\\
\hline

 & \par
 \parbox{12cm}{
	\begin{itemize}[noitemsep, topsep=2pt]
		\item[] 
		\begin{itemize}[noitemsep, topsep=2pt]
			\item For solenoids, a tutorial level will be included where magnetism will be exhibited as follows: a solenoid connected with a battery will be shown. An image of iron nails kept nearby shall be animated to move nearer the solenoid, depicting attraction. In the tutorial, a brief description of a magnet and why it attracts only certain materials.
		\end{itemize}
	\end{itemize}	 
 }\\
 \hline

@@

\end{tabularx}
\end{center}
\textbf{\underline{Note:} I will have to slow down my work during the month of May and/or June(mid May - End of May probably)} due to my final semester exams.
\bigskip\bigskip\bigskip\bigskip

@@

\item {Added option to change case of letter to find in Letter-In-Word activity:\\
\href{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}{https://commits.kde.org/gcompris/7c769594a5372e560904511404e2d1e156904050}}
\end{itemize}
\bigskip
\textbf{Website: }\href{mouri11.github.io}{mouri11.github.io}\\
\textbf{Contact Info:}\\
\textbf{Email: }{Rohit Das $[$rohit.das950@gmail.com$]$}\\
\textbf{IRC Nick: } mouri11
